### 2018-01-22 study-dataset.tex
minor fixes
working on the clustering section

We select the simulation results and validation analysis done by \citet{Taborda_2014_BSSA} as our reference dataset. In that study, the authors carried out deterministic simulations for the 2008 \eqmag{w} 5.4 Chino Hills, California, earthquake using a finite-element approach. The simulations, done for a kinematic finite-fault model of the earthquake, were computed for a maximum frequency \fmaxeq{4} and a minimum shear wave velocity \vsmineq{200}. In total, \citet{Taborda_2014_BSSA} did three simulations, each for a different velocity model \citep[CVM-S4, CVM-H, CVM-H+GTL, see][]{Small_2017_SRL}. The modeling domain covered an area of \adomain{180}{135}{km} that included all the major sedimentary basins and other relevant geologic structures in the greater Los Angeles region. Their validation analysis consisted of comparisons with data recorded during the event at 336 ground motion monitoring stations, for the three component of motion (EW, NS, and UD). The simulation domain and the stations used for the analysis are shown in Figure \ref{fig:chino-hills}, and the validation results obtained by \citet{Taborda_2014_BSSA} for the GOF analysis of the broadband signals using \citeauthor{Anderson_2004_Proc}'s approach is shown in Figure \ref{fig:ref-gof-maps} for the three simulation sets.

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-02}
    \caption{Validation results obtained by \citet{Taborda_2014_BSSA} in the form of GOF values across the region of interest obtained from comparisons between simulations for three different velocity models and data recorded at ground motion monitoring stations.}
    \label{fig:ref-gof-maps}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/pdf/figure-03}
    \caption{Statistical distribution of the GOF scores used in this study based on the validation results obtained by \citet{Taborda_2014_BSSA} shown in the form of box-plots for each metric (C1 through C11, see Table \ref{tab:metrics}), velocity model (CVM-S, CVM-H, and CVM-H+GTL), and component of motion (NS, EW, UD). In each case, the median is indicated by a notch in the box of the central quartiles, and the lines represent the interquartile range (Q3-Q1), with outliers shown as scattered dots.}
    \label{fig:data-box-plot}
\end{figure}

>>>>

We select the simulation results and validation analysis done by \citet{Taborda_2014_BSSA} as our reference dataset, hereafter the dataset. In that study, the authors carried out deterministic simulations for the 2008 \eqmag{w} 5.4 Chino Hills, California, earthquake using a finite-element approach. The simulations, done for a kinematic finite-fault model of the earthquake, were computed for a maximum frequency \fmaxeq{4} and a minimum shear wave velocity \vsmineq{200}. In total, \citet{Taborda_2014_BSSA} did three simulations, each for a different velocity model \citep[CVM-S4, CVM-H, CVM-H+GTL, see][]{Small_2017_SRL}. The modeling domain covered an area of \adomain{180}{135}{km} that included all the major sedimentary basins and other relevant geologic structures in the greater Los Angeles region. Their validation analysis consisted of comparisons with data recorded during the event at 336 ground motion monitoring stations, for the three component of motion (EW, NS, and UD). The simulation domain and the stations used for the analysis are shown in Figure \ref{fig:chino-hills}, and a sample of the validation results obtained by \citet{Taborda_2014_BSSA} using \citeauthor{Anderson_2004_Proc}'s approach is shown in Figure \ref{fig:ref-gof-maps}. This second figure, in particular, shows the spatial distribution of GOF scores (interpolated from the values at each station) for the comparison of the broadband synthetics and data, averaged for all metrics, and the three component of motion. This type of so-called GOF maps are commonly used in validation studies.

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-02}
    \caption{Validation results obtained by \citet{Taborda_2014_BSSA} in the form of GOF values across the region of interest obtained from comparisons between simulations for three different velocity models and data recorded at ground motion monitoring stations.}
    \label{fig:ref-gof-maps}
\end{figure*}
% 
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/pdf/figure-03}
    \caption{Statistical distribution of the GOF dataset obtained from \citet{Taborda_2014_BSSA} shown in the form of box-plots for each metric (C1 through C11, see Table \ref{tab:metrics}), velocity model (CVM-S, CVM-H, and CVM-H+GTL), and component of motion (NS, EW, UD). In each case, the median is indicated by a notch in the box of the central quartiles, and the lines represent the interquartile range, with outliers shown as scattered dots.}
    \label{fig:data-box-plot}
\end{figure}

@@
